### 2014-10-22 old_notes/notes_signaling_model_11_01_12.tex
ive added code for tracking mutual information over time and changed figures a bit

\begin{center}
{\bf \LARGE{Development of a Signaling Network}}
\vspace{10pt}
\\ Eleanor Brush
\\ October 03, 2012
\end{center}

@@

The Jacobian of this system is given by
$$J(x,y)=\left(\begin{array}{cccc} 
-e & br'(y+T)
\\ br'(x+T) & -e
\end{array}\right)$$
Letting $\tau=Tr(J(x,y))$ and $\Delta=\text{det}(J(x,y)),$ we see that $\tau=-2e$ and $\Delta=e^2-b^2r'(y+T)r'(x+T)$.  Since $e>0$, $\tau<0$ and any fixed point will be a saddle point, a stable sink, or a stable spiral, depending on the sign of $\Delta$.  
\begin{align*}
\Delta<0 &\Leftrightarrow e^2-b^2r'(y+T)r'(x+T)<0 
\\&\Leftrightarrow e<b\sqrt{r'(y+T)r'(x+T)} \text{ since } e,b, \text{ and } r'(y+T)r'(x+T)\geq0
\\ &\Leftrightarrow \left\{\begin{array}{cccc}
b>0 & \text{ if } e=0
\\ b>2\epsilon e & \text{ if } e>0
\end{array}\right.
\end{align*}
Therefore, if there is a fixed point with $r'(y+T)\neq 0$ and $r'(x+T)\neq 0$ (i.e. the isoclines cross where their slopes are not zero), the fixed point is a saddle and there are two other stable fixed points only if $b>2\epsilon e$.  Other conditions are required, as well.  In the following, we let $c=\frac{f}{e}$.  Then we also need
\begin{align}
-T+\epsilon&<-c+\frac{b}{e}r(c+T) \label{cond1} 
\\ -T-\epsilon&>-c+\frac{b}{e}r(c+\frac{b}{e}+T) \label{cond2}
\end{align}

These lead to the following conditions on $\frac{f}{e}=c$:
\begin{align}
(\ref{cond1}) \Rightarrow -T+\epsilon&<-c-\frac{b}{2\epsilon e}c-\frac{bT}{2\epsilon e}+\frac{b}{2e} \notag
\\ \Rightarrow c&<\left(\frac{2\epsilon e-b}{2\epsilon e+b}\right)T-\frac{2\epsilon^2e}{2\epsilon e+b}+\frac{\epsilon b}{2\epsilon e+b}=:M \label{xmax}
\\ (\ref{cond2}) \Rightarrow -T-\epsilon&>-c-\frac{b}{2\epsilon e}c-\frac{b^2}{2\epsilon e^2}-\frac{bT}{2\epsilon e}+\frac{b}{2e} \notag
\\ \Rightarrow c&>\left(\frac{2\epsilon e-b}{2\epsilon e+b}\right)T+\frac{2\epsilon^2e-b^2/e}{2\epsilon e +b}+\frac{\epsilon b}{2\epsilon e+b}=:m \label{xmin}
\end{align}
Note that $m<M$ if and only if $b>2\epsilon e$, so that $m$ and $M$ are valid lower and upper bounds on $x$ only if $b$ is sufficiently large for a saddle point to exist.  Equations (\ref{xmax}) and (\ref{xmin}) can be rewritten to provide bounds on $T$ that allow a bifurcation to occur:
\begin{align}
(\ref{xmax}) \Rightarrow(2\epsilon e-b)T&>  (2\epsilon e+b)c +2\epsilon^2e-\epsilon b \notag
\\ \Rightarrow  T&<\frac{(2\epsilon e+b)c+2\epsilon^2e-\epsilon b}{2\epsilon e-b}  \notag
\\ \Rightarrow T&< \frac{ 2\epsilon e(c+\epsilon)+b(c-\epsilon)}{2\epsilon e-b}\label{tmax}
\\(\ref{xmin}) \Rightarrow (2\epsilon e-b)T&< (2\epsilon e+b)c-2\epsilon^2e+b^2/e-\epsilon b \notag
\\ \Rightarrow  T&>\frac{(2\epsilon e+b)c-2\epsilon^2e+b^2/e-\epsilon b}{2\epsilon e-b}\notag
\\ \Rightarrow T&> \frac{2\epsilon e(c-\epsilon)+b(c-\epsilon+b/e)}{2\epsilon e-b} \label{tmin}
\end{align}
If the equivalent conditions (\ref{cond1}),(\ref{xmax}),(\ref{tmax}) are violated, there can be no stable fixed point with animal 1 signaling at a nonzero rate and animal 2 not signaling because the difference in fighting ability is too great or the threshold below which signaling occurs is too low.

Another interesting phenomenon is the possibility of each animal signaling the other at a non-zero rate.  In order for this to occur, we need $\dot{x}(x,-\frac{f}{e})<0$ for al $x>x^*$ and in particular for $x=-T+\epsilon$ so that
\begin{align*}
-e(-T+\epsilon)+f+br(-\frac{f}{e}+T)&<0
\\ \Rightarrow-T+\epsilon&>c+\frac{b}{e}r(-\frac{f}{e}+T)
\\ \Rightarrow -T+\epsilon&>c+\frac{b}{e}\left(\frac{c}{2\epsilon}-\frac{T}{2\epsilon}+\frac{1}{2}\right)
\\ \Rightarrow \frac{(b-2\epsilon e)}{2\epsilon e}T&>c-\epsilon+\frac{bc}{2\epsilon e}+\frac{b}{2e}
\\ \Rightarrow (b-2\epsilon e)T&>2\epsilon e(c-\epsilon)+bc+b\epsilon
\\ \Rightarrow T&<\frac{2\epsilon e(\epsilon -c)-b(c+\epsilon)}{2\epsilon e-b} 
\end{align*}
where the last inequality follows because this can only happen if $b<2\epsilon e$.  (The condition $b<2\epsilon e$ is equivalent to the slope of the $x$ isocline being steeper than the slop of the $y$ isocline where they have non-zero slopes.  Otherwise, if $x$ and $y$ are both signaling at non-zero rates, a bifurcation will occur.)

Note that if $f>0$ so that $\frac{f}{e}>-T-\epsilon,$ there can be no steady state with animal $1$ signaling at rate $=1$.  The possible steady states are as follows:
\begin{enumerate}
\item Neither animal signaling:
\begin{align*}
\Rightarrow -T+\epsilon< \frac{f}{e} \text{ and } -T+\epsilon<-\frac{f}{e}
\\ \Rightarrow T>\epsilon-\frac{f}{e} \text{ and } T> \epsilon+\frac{f}{e}
\\ \Rightarrow T>\epsilon+\frac{f}{e}
\end{align*}
\item Animal 1 not signaling, animal 2 signaling at a rate $\in(0,1)$:
\begin{enumerate}
\item 
\begin{align*}
-T-\epsilon<-\frac{f}{e}
\\ \Rightarrow T>\frac{f}{e}-\epsilon
\end{align*}
\item \begin{align*}
\frac{f}{e}+\frac{b}{e}r\left(-\frac{f}{e}+T\right)>-T+\epsilon&>\max\left\{-\frac{f}{e}+\frac{b}{e}r\left(\frac{f}{e}+T\right),-\frac{f}{e}\right\}
\\ \Rightarrow \epsilon-\frac{f}{e}-\frac{b}{e}r\left(-\frac{f}{e}+T\right)<T&<\epsilon-\max\left\{-\frac{f}{e}+\frac{b}{e}r\left(\frac{f}{e}+T\right),-\frac{f}{e}\right\}
\\ \Rightarrow \epsilon-\frac{f}{e}-\frac{b}{e}r\left(-\frac{f}{e}+T\right)<T&<\min\left\{\epsilon+\frac{f}{e}-\frac{b}{e}r\left(\frac{f}{e}+T\right),\epsilon+\frac{f}{e}\right\}
\\ \Rightarrow \left\{\begin{array}{cccc} 
\frac{2\epsilon e(\epsilon -\frac{f}{e})+b(-\frac{f}{e}-\epsilon)}{2\epsilon e-b}<T<\epsilon+\frac{f}{e} &\text{ if } b<2\epsilon e
\\\frac{2\epsilon e(\epsilon +\frac{f}{e})+b(\frac{f}{e}-\epsilon)}{2\epsilon e-b}<T<\epsilon+\frac{f}{e} &\text{ if } b>2\epsilon e
\end{array}\right.
\end{align*}
\end{enumerate}
\item Animal 1 not signaling, animal 2 signaling at rate $=1$:
\begin{enumerate}
\item 
\begin{align*}
-T-\epsilon&>-\frac{f}{e}
\\ \Rightarrow T&<\frac{f}{e}-\epsilon
\end{align*}
Therefore, for the following condition we assume that $\frac{f}{e}-\epsilon>0$ so that $\epsilon-\frac{f}{e}<0$.
\item 
\begin{align*}
\frac{f}{e}+\frac{b}{e}>-T+\epsilon&>-\frac{f}{e}+\frac{b}{e}r\left(\frac{f}{e}+T\right)
\\ \Rightarrow \epsilon-\frac{f}{e}-\frac{b}{e}<T&<\epsilon+\frac{f}{e}-\frac{b}{e}r\left(\frac{f}{e}+T\right)
\\ \Rightarrow T&\left\{\begin{array}{cccc}
<\frac{2\epsilon e(\epsilon +\frac{f}{e})+b(\frac{f}{e}-\epsilon)}{2\epsilon e-b} & \text{ if } b<2\epsilon e
\\ >\frac{2\epsilon e(\epsilon +\frac{f}{e})+b(\frac{f}{e}-\epsilon)}{2\epsilon e-b} & \text{ if } b>2\epsilon e
\end{array}\right.
\\ \Rightarrow
0<T&<\frac{f}{e}-\epsilon
\end{align*}
\end{enumerate}
\item Both animals signaling at a non-zero rate, but only one steady state:
\begin{enumerate}
\item $b<2\epsilon e$ ensures that there is no unstable equilibrium, i.e. there is only one equilibrium
\item 
\begin{align*}
-T+\epsilon&>-\frac{f}{e}+\frac{b}{e}r(-\frac{f}{e}+T)
\\ \Rightarrow T&<\frac{2\epsilon e(\epsilon -\frac{f}{e})-b(\frac{f}{e}+\epsilon)}{2\epsilon e-b} 
\end{align*}

\item Two stable equilibria, one with animal 1 signaling at a non-zero rate and animal 2 not signaling and one with animal 1 not signaling and animal 2 signaling at a non-zero rate:
\begin{enumerate}
\item $b>2\epsilon e$
\item 
\begin{align*}
-T+\epsilon&<-\frac{f}{e}+\frac{b}{e}r\left(\frac{f}{e}+T\right)
\\ \Rightarrow T&>\epsilon+\frac{f}{e}-\frac{b}{e}r\left(\frac{f}{e}+T\right)
\\ \Rightarrow T&<\frac{ 2\epsilon e(\epsilon+\frac{f}{e})+b(\frac{f}{e}-\epsilon)}{2\epsilon e-b}\end{align*}
\item 
\begin{align*}
-T-\epsilon&>-\frac{f}{e}+\frac{b}{e}r\left(\frac{f}{e}+\frac{b}{e}+T\right)
\\ \Rightarrow T&>\frac{2\epsilon e(\frac{f}{e}-\epsilon)+b(\frac{f}{e}+\frac{b}{e}-\epsilon)}{2\epsilon e-b}
\\ \Rightarrow T&>0 \text{ if } b>2\epsilon e \text{ and } \frac{f}{e}<\epsilon 
\end{align*}
\end{enumerate}
(Two stable equilibria, one with animal 1 signaling at a non zero rate and animal 2 not signaling and the other with animal 1 not signaling and animal 2 signaling at rate $=1$ would require $T<\frac{f}{e}-\epsilon$, which is negative if there is a bifurcation, so that this is not possible.

Two stable equilibria, one with animal 1 signaling at a non zero rate and animal 2 not signaling and the other with animal 1 signaling at a non-zero rate and animal 2 signaling at rate $=1$ would require $T<\epsilon-\frac{f}{e}-\frac{b}{e}\Rightarrow T<-\epsilon-\frac{f}{e}$, which is negative if there is a bifurcation, so that this is not possible.)
\item A single steady state with animal 1 signaling at a non-zero rate is not possible.
\end{enumerate}

Let $$\psi(b)=\frac{2\epsilon e(\epsilon -\frac{f}{e})-b(\frac{f}{e}+\epsilon)}{2\epsilon e-b} \text{ and } \varphi(b)=\frac{ 2\epsilon e(\epsilon+\frac{f}{e})+b(\frac{f}{e}-\epsilon)}{2\epsilon e-b}$$
Then, there are three general cases, depending on the magnitude of $\frac{f}{e}$ (Figure \ref{bifurcation}):
\begin{enumerate}
\item $\frac{f}{e}<\epsilon$:
\begin{enumerate}
\item neither animal signaling if $T>\epsilon+\frac{f}{e}$
\item animal 1 not signaling and animal 2 signaling at a non-zero rate if $T<\epsilon+\frac{f}{e}$ and 
$$T>\left\{\begin{array}{cccc}
\varphi(b) & \text{ if } b>2\epsilon e
\\ \psi(b) & \text{ if } b<2\epsilon e
\end{array}\right.$$

@@

\begin{figure}
\begin{center}
\includegraphics[width=1\textwidth]{bifurc_diagram.pdf}
\end{center}
\caption{{\bf The equilibria of the signaling model as a function of feedback level, $b$, and signaling threshold, $T$.} For both plots, $e=.5$, $\epsilon=.1$. As $f$ increases from less than $\epsilon e$ to greater than $\epsilon e$, the possible equilibria change.  \label{bifurcation}}
\end{figure}

%\frac{(2\epsilon e)(\epsilon-\frac{f}{e})-b(\frac{f}{e}+\epsilon)}{2\epsilon e-b}
%\begin{table}
%\caption{Possible equilibrium of the signaling model without stochastic dynamics.}
%\begin{tabular}{@{}lllll@{}}
%\toprule
%State & Condition on $b$ & Condition on $T$
%\\\midrule animal $1$ not signaling, animal $2$ signaling at a non-zero rate & & $T>\frac{f}{e}-\epsilon$
%\end{tabular}
%\end{table}

>>>>

\begin{center}
{\bf \LARGE{Development of a Signaling Network}}
\vspace{10pt}
\\ Eleanor Brush
\\ November 01, 2012
\end{center}

@@

The Jacobian of this system is given by
$$J(x,y)=\left(\begin{array}{cccc} 
-e & br'(y+T)
\\ br'(x+T) & -e
\end{array}\right)$$
Letting $\tau=Tr(J(x,y))$ and $\Delta=\text{det}(J(x,y)),$ we see that $\tau=-2e$ and $\Delta=e^2-b^2r'(y+T)r'(x+T)$.  Since $e>0$, $\tau<0$ and any fixed point will be a saddle point, a stable sink, or a stable spiral, depending on the sign of $\Delta$.  
\begin{align*}
\Delta<0 &\Leftrightarrow e^2-b^2r'(y+T)r'(x+T)<0 
\\&\Leftrightarrow e<b\sqrt{r'(y+T)r'(x+T)} \text{ since } e,b, \text{ and } r'(y+T)r'(x+T)\geq0
\\ &\Leftrightarrow \left\{\begin{array}{cccc}
b>0 & \text{ if } e=0
\\ b>2\epsilon e & \text{ if } e>0
\end{array}\right.
\end{align*}
Therefore, if there is a fixed point with $r'(y+T)\neq 0$ and $r'(x+T)\neq 0$ (i.e. the isoclines cross where their slopes are not zero), the fixed point is a saddle and there are two other stable fixed points only if $b>2\epsilon e$.  Figure \ref{basins} shows the basins of attraction for the two stable nodes when the system is bistable.

\begin{figure}
\begin{center}
\includegraphics[width=6in]{basins_of_attraction.eps}
\end{center}
\caption{{\bf The basins of attraction for each of the two stable nodes in the case when the system is bistable.} The fixed points are marked in red circles.  The isoclines are marked as blue lines.  The red line separates the basin of attraction for the fixed point where the stronger animal is signaling (above the red line) and the fixed point where the weaker animal is signaling (below the red line). \label{basins}}
\end{figure}

Let $$\psi(b)=\frac{2\epsilon e(\epsilon -\frac{f}{e})-b(\frac{f}{e}+\epsilon)}{2\epsilon e-b} \text{ and } \varphi(b)=\frac{ 2\epsilon e(\epsilon+\frac{f}{e})+b(\frac{f}{e}-\epsilon)}{2\epsilon e-b}$$
Then, there are three general cases, depending on the magnitude of $\frac{f}{e}$ (Figures \ref{bifurcation}-\ref{wireframe}):
\begin{enumerate}
\item $\frac{f}{e}<\epsilon$:
\begin{enumerate}
\item neither animal signaling if $T>\epsilon+\frac{f}{e}$
\item animal 1 not signaling and animal 2 signaling at a non-zero rate if $T<\epsilon+\frac{f}{e}$ and 
$$T>\left\{\begin{array}{cccc}
\varphi(b) & \text{ if } b>2\epsilon e
\\ \psi(b) & \text{ if } b<2\epsilon e
\end{array}\right.$$

@@

In the above analysis, we considered fixed values of $b$ and $f$ and determined how the value of the threshold $T$ affected the behavior of the system.  In practice, it seems more reasonable for there to be fixed values of $T$ and $b$ (i.e. psychologically all animals in the population are more or less the same), but the difference in fighting ability will vary from pair to pair.  If this is the case, then we need to determine how the value of $f$ affects the behavior of the system (Figures \ref{f_heatmap} and \ref{wireframe}):
\begin{enumerate}
\item $T>\epsilon$ (so that no animal ever signals when he has a positive estimate of its own dominance):
\begin{enumerate}
\item neither animal signals if $f<e(T-\epsilon)$ 
\item the weaker animal signals at a non-zero rate if $f>e(T-\epsilon)$ and $f<e(T+\epsilon)$
\item the weaker animal signals at a maximal rate if $f>e(T+\epsilon)$
\end{enumerate}
\item $T<\epsilon$
\begin{enumerate}
\item both signal if $b<2\epsilon e$ and $f<\frac{(2\epsilon e-b)e(\epsilon-T)}{2\epsilon e+b}$
\item the system is bistable with two equilibria, and in either case one animal doesn't signal and the other signals at a non-zero rate if $b>2\epsilon e$ and $f<\frac{(b-2\epsilon e)e(\epsilon-T)}{2\epsilon e+b}$
\item the weaker animal signals at a non-zero rate if $f>\left|\frac{(b-2\epsilon e)e(\epsilon-T)}{2\epsilon e+b}\right|$ and $f<e(T+\epsilon)$
\item the weaker animal signals at a maximal rate if $f>e(T+\epsilon)$
\end{enumerate}
\end{enumerate}

%\begin{figure}
%\begin{center}
%\includegraphics[width=1\textwidth]{bifurc_diagram.pdf}
%\end{center}
%\caption{{\bf The equilibria of the signaling model as a function of feedback level, $b$, and signaling threshold, $T$.} For both plots, $e=.5$, $\epsilon=.1$. As $f$ increases from less than $\epsilon e$ to greater than $\epsilon e$, the possible equilibria change.  \label{bifurcation}}
%\end{figure}
%
%\begin{figure}
%\begin{center}
%\includegraphics[width=6in]{heatmap_bifurcation_v1.eps}
%\end{center}
%\caption{{\bf The critical value of the parameter $f$ as a function of $b$ and $T$.}  For a given pair of values of $b$ and $T$, if $f$ is above the value indicated by the heatmap the equilibrium of the system is such that the weaker animal signals at a non-zero rate and the stronger animal doesn't signal.  If $f$ is below the value indicated by the heatmap, the equilibria is as indicated by the text. \label{f_heatmap}}
%\end{figure}
%
%\begin{figure}
%%\includegraphics[]{wireframe_bifurcation_v1.eps}
%\includegraphics[width=\textwidth]{wireframe_bifurcation_v2.eps}
%\caption{{\bf The dependence of the equilibria of the system on all three parameters, $b$, $T$, and $f$.} $T$ is on the $x$ axis, $b$ is on the $y$ axis and $f$ is on the $z$ axis.  If $f$ is above the upper plane, the equilibrium is such that the weaker animal signals at a maximal rate.  If $f$ is between the two planes, the equilibrium is such that the weaker animal signals at a non-zero rate.  If $f$ is below the lower plane, the equilibria depends on $b$ and $T$ as indicated by Figures \ref{bifurcation} and \ref{f_heatmap}. \label{wireframe}}
%\end{figure}

Suppose these dynamics are going on between every pair of animals in a group where the fighting abilities are drawn from some distribution.  How will a network of signals exchanged develop?  Let's first look at a simple metric of such a network: the number of signalers sending signals to a given animal.  
\begin{align*}
P(n \text{ signalers})=\int P(x)P(n \text{ signalers}|x)dx \text{ where $x$ is the fighting ability of a focal animal}
\end{align*}
If $T>\epsilon$ then animal $i$ signals to animal $j$ if and only if $f_j-f_i>e(T-\epsilon)$.  Therefore,
\begin{align*}
P(n \text{ signalers}|x)={N-1 \choose n}P(x-y>e(T-\epsilon))^nP(x-y<e(T-\epsilon))^{(N-1-n)}
\end{align*}
where $N$ is the total number of animals in the group and we use the binomial distribution to express the probability of $n$ signalers as a function of the probability of one of the other $N-1$ animals signaling, which we assume to be independent events.

At first, we will assume that fighting ability is drawn uniformly from some range $[-L,L]$.  In order for signaling to be possible, we need $e(T-\epsilon)<2L$.
\begin{align*}
\\ \Rightarrow P(x-y>e(T-\epsilon))&=\frac{L+x-e(T-\epsilon)}{2L} \\ \text{ and } P(x-y<e(T-\epsilon))&=\frac{L-x+e(T-\epsilon))}{2L}
\\ \Rightarrow P(n \text{ signalers}|x)&={N-1\choose n}\left(\frac{L+x-e(T-\epsilon)}{2L}\right)^n\left(\frac{L-x+e(T-\epsilon))}{2L}\right)^{(N-1-n)}
\\ \Rightarrow P(n \text{ signalers})&=\int_{-L+e(T-\epsilon)}^L\frac{1}{2L}{N-1\choose n}\left(\frac{L+x-e(T-\epsilon)}{2L}\right)^n\left(\frac{L-x+e(T-\epsilon))}{2L}\right)^{(N-1-n)}dx
\\ &=\int_0^{1-\frac{e(T-\epsilon)}{2L}}{N-1\choose n}z^n(1-z)^{(N-1-n)}dz \text{ using $z=\frac{L+x-e(T-\epsilon)}{2L}$}
\\ &={N-1\choose n}\int_0^{1-\frac{e(T-\epsilon)}{2L}}z^n(1-z)^{(N-1-n)}
\\ &={N-1 \choose n} B\left(1-\frac{e(T-\epsilon)}{2L};n+1,N-n\right) \text{ where $B(c;x,y)=\int_0^cz^{x-1}(1-z)^{y-1}dz$}  
\\&={N-1\choose n}B(n+1,N-n)F\left(1-\frac{e(T-\epsilon)}{2L};n+1,N-n\right)
\\&=\frac{1}{N}F\left(1-\frac{e(T-\epsilon)}{2L};n+1,N-n\right) \tag{$\star$} \label{STAR}
\end{align*} 
where $F(x;\alpha,\beta)=\int_0^x\frac{z^{\alpha-1}(1-z)^{\beta-1}}{B(\alpha,\beta)}dz$ is the cumulative distribution function of the Beta distribution and $B$ is the Beta function with shape parameters $\alpha$ and $\beta$.

If $n=0$, we have to make a small correction:
\begin{align*}
P(0 \text{ signalers})&=\frac{1}{N}F\left(1-\frac{e(T-\epsilon)}{2L};1,N\right)+\frac{e(T-\epsilon)}{2L}
\end{align*}
since if $x\in [-L,-L+\frac{e(T+\epsilon)}{2L}],$ the animal will receive no signals.

Suppose $T=\epsilon$ so signaling at a non-zero rate starts as soon as an animal's estimate is negative.  Then 
\begin{align*}
P(n \text{ signalers})&=\frac{1}{N}F(1-0;n+1,N-n)
\\&=\frac{1}{N}F(1;n+1,N-n)
\\&=\frac{1}{N}
\end{align*}
so the distribution of number of signalers is uniform over the possibilities $0,1,\dots,N-1$.  If $T\gneq \epsilon$, having fewer signalers is more probable and having more signalers is less probably.  The probability distribution of number of signalers for a small set of parameters is shown in Figure \ref{derived_sig_probs}.

\begin{figure}
\includegraphics[width=6in]{distributions_of_signals_received_uniform.pdf}
\caption{The probability distribution of number of signalers, assuming a uniform distribution of fighting abilities, as derived in Eq. (\ref{STAR}).  \label{derived_sig_probs}}
\end{figure}
